### 2017-10-15 mcmc.tex
ref

The key idea here is that if the proposal distribution is too narrow---%
  it proposes steps too small---%
  almost all steps will be accepted (REFERENCE ALGORITHM HERE),
  but it will take a long time to move anywhere because of timidity.
If the proposal distribution is too wide---%
  it proposes steps too large---%
  the moves will cover parameter space easily,
  but almost no steps will be accepted;
  it will tend to jump to much lower probability regions.
There is a Goldilocks step size (proposal distribution root-variance) that is ``just right''.
In one dimension this might be easy to find,
  but, as we say, in large numbers of dimensions,
  there is a lot of freedom in choosing the parameters of the distribution.

>>>>

The key idea here is that if the proposal distribution is too narrow---%
  it proposes steps too small---%
  almost all steps will be accepted (recall the acceptance-rejection step from \sectionname~\ref{sec:MH})
  but it will take a long time to move anywhere because of timidity.
If the proposal distribution is too wide---%
  it proposes steps too large---%
  the moves will cover parameter space easily,
  but almost no steps will be accepted;
  it will tend to jump to much lower probability regions.
There is a Goldilocks step size (proposal distribution root-variance) that is ``just right''.
In one dimension this might be easy to find,
  but, as we say, in large numbers of dimensions,
  there is a lot of freedom in choosing the parameters of the distribution.
